Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\begin{abstract} 
%CAUSE --> EFFECT --> MOTIVATION (P1)
  A critical aspect of multiphase flows in porous media is the displacement efficiency that measures the quantity of fluid that can be pushed by another fluid due to pressure gradient. Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which simulation of immiscible fluid displacement dynamics may help mitigating water resources contamination and improving hydrocarbons production. Due to large fluids' viscosity ratio, flow instabilities may arise leading to formation and growth of fingers with strong impact on the efficiency of oil and gas exploration.

%CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
The main aim of this work is to numerically investigate

>>>>

\begin{abstract} 
%CAUSE --> EFFECT --> MOTIVATION (P1)
  A critical aspect of multiphase flows in porous media is the displacement efficiency that measures the amount of fluid that can be pushed by another fluid driven by pressure gradient. Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which understandiing the dynamics of immiscible fluid displacement may help mitigating water resources contamination and improving hydrocarbons production. Due to the large viscosity ratio, flow instabilities at fluids' interface may arise leading to formation and growth of fingers, with strong impact on the displacement efficiency.  
%CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)

The main aim of this work is to numerically investigate
